---
title: "AB_Testing_Analysis_1"
author: "Jen Yu Ou"
date: "2023-10-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Source:
  https://www.kaggle.com/datasets/faviovaz/marketing-ab-testing/
  
  
## Data information:
  * Index: Row index
  * user id: User ID (unique)
  * test group: If "ad" the person saw the advertisement, if "psa" they only saw the public service announcement
  * converted: If a person bought the product then True, else is False
  * total ads: Amount of ads seen by person
  * most ads day: Day that the person saw the biggest amount of ads
  * most ads hour: Hour of day that the person saw the biggest amount of ads
  
# Prepare the library

```{r}
library(readr)
library(dplyr)
library(tidyverse)
library(readr)
library(corrplot)
library(mosaic)
library(lemon)
library(devtools)
library(hablar)
```

# Step 1: Loading  and examining data

```{r}
marketing_AB <- read_csv("D:/Learn/GitFile/AB_Testing_Analysis_1/marketing_AB.csv")
M <-marketing_AB %>% 
  arrange(desc(`total ads`))

group_in_test<-M %>% 
  group_by(`test group`) %>% 
  summarize(ad_group = count(`test group`))
group_in_day<-M %>% 
  group_by(`most ads day`,`test group` ) %>% 
  summarize(ad_group = count(`test group`))
group_in_test

M_num <-marketing_AB %>% 
  mutate(test_group_num = ifelse(
    `test group` == 'ad', 1, 0)) %>% 
  mutate(converted_num = ifelse(
    converted == 'TRUE',1,0)) %>% 
  mutate (most_ads_day_num = ifelse(
    `most ads day` == 'Monday', 1, ifelse(
      `most ads day` == 'Tuesday', 2, ifelse(
        `most ads day` == 'Wednesday', 3, ifelse (
          `most ads day` == 'Thursday', 4, ifelse (
            `most ads day` == 'Friday', 5, ifelse (
              `most ads day` == 'Saturday', 6, 7))))))) %>% 
  subset(select = -c(`test group`,`converted`, `most ads day`))

# Check which perimeter has relationship with converted rate
Corr_M<- cor(M_num)
Corr_M_table<-round(Corr_M, 2)
corrplot(Corr_M, method="circle", type="upper", sig.level = 0.05, insig = "blank")
#  total ads has more relationship with converted rate

# Get the information of how many converted under the total ads and the test group
M_TTADS_TTCONV<- M_num %>%
  group_by(`total ads`, test_group_num) %>% 
  reframe(total_converted = sum(converted_num)) %>% 
  arrange(desc(`total ads`))
M_Final<- M_TTADS_TTCONV%>% 
  group_by(`total ads`) %>% 
  filter(n()>1)  ## get the data that has records both AD and PSA
M_Final

# See the trend of the organized data
Trend<-ggplot(M_Final, aes(x=`total ads`, y=total_converted)) +
        geom_point(aes(color =  as.factor(test_group_num))) + 
        guides(color = guide_legend(title = "Test Categories")) +
        scale_colour_discrete(labels = c("PSA", "AD") ) +
        ggtitle("Trends of Total ADs vs Total Converted")
Trend

```

        * From the data examination, we can know that:
              1. AD and PSA have a huge difference between the size, and we have to resample from the data to let the size more similar
              2. Converted rate has more relationship with total ads
              3. Even though most converted happens when total ads less than 375, we still need to make sure that all data was considerated so I choose to use total 692 data to run the statistical test (ADs = 346, PSA = 346)

# Step 2: Statisitc test
        H0: converted rate of PSA >= converted rate of AD
        H1: converted rate of PSA < converted rate of AD (Alternative Hypothesis)
        
        * significant level(α) = 0.05
```{r}
ad_sample<- M_Final %>% 
  filter(test_group_num == 1)
psa_sample<- M_Final %>% 
  filter(test_group_num == 0)


prop.test(
  x =c(sum(psa_sample$total_converted), sum(ad_sample$total_converted)),
  n = c(sum(psa_sample$`total ads`), sum(ad_sample$`total ads`)),
  alternative = "less",  # test PSA is less than AD or not
  correct = FALSE  # No Yates' continuity correction
)

```
      
# Step 3: Analyze the reault:
        * p-value is closed to 0 (<< α) so the chance of PSA converted rate > AD converted rate is really small so we can reject H0
        
        

# Conclusion: The PSA method is not better than AD
      

      
      
      
      
      
      
      
      
      
  

